The \dealii Library, Version 9.1

### 2019-05-10 9.1/paper.tex
More ideas.
Add another note about the BR element.

The major changes of this release are:
\begin{itemize}
\item Improved support for automatic and symbolic differentiation;
\item Full support for $hp$ adaptivity in parallel computations;
\item Four new tutorial programs step-61, step-62, step-63, step-64,
  as well as one new code gallery program.
\end{itemize}
These will all be discussed in more detail in the
following section. There are a number of other noteworthy changes in this release:
\begin{itemize}
\item A number of bug fixes and performance improvements to the
  matrix-free framework and related geometric multigrid solvers. In
  particular, the implementation of the Chebyshev iteration, an often
  used smoother in the matrix-free context, has been revised to reduce
  vector accesses. This speeds up matrix-free
  multigrid solvers by up to 10-15\% on geometries with affine
  (parallelogram and parallelpiped) cells, and up to
  5\% on geometries with cells bounded by curved edges and faces.
\marginpar{Luca: Please expand}
\item ParsedConvergenceTable.  
\item The \texttt{FE\_BernardiRaugel} class implements the
  non-standard Bernardi-Raugel (BR) element that can be used as one part of
  a stable velocity/pressure pair for the Stokes equation
  \cite{BR85}. The BR element can be seen as either an enriched
  version of the $Q_1^d$ element with added bubble functions on each
  edge (in 2d) or face (in 3d), or as a reduced version of the $Q_2^d$
  element. It addresses the fact that the $Q_1^d\times Q_0$
  combination is not inf-sup stable (requiring a larger velocity
  space), and that the $Q_2^d\times Q_1$ combination is stable but
  sub-optimal since the velocity space is too large relative to the
  pressure space to provide additional accuracy commensurate with the
  cost of the large number of velocity unknowns. The BR space is
  intermediate to the $Q_1^d$ and $Q_2^d$ spaces.

\item The \texttt{FE\_NedelecSZ} class is an alternative
  implementation of the ideas behind the N{\'e}d{\'e}elec element. It is based
  on the work of Zaglmayr \cite{Zag06} and overcomes the
  sign conflict issues present in traditional N{\'e}d{\'e}lec
  elements that arise from the edge and face parameterizations used
  in the basis functions. Therefore, this element should provide
  consistent results for general quadrilateral and hexahedral
  elements for which the relative orientations of edges and faces as
  seen from all adjacent cells are often difficult to establish.
  The way this element addresses the sign conflict problem is to assign
  local edges and faces a globally defined orientation. The
  implementation is described in \cite{Kynch2017}.
\end{itemize}

@@

@@

\dealii can interface with many other libraries:
\begin{multicols}{3}
\begin{itemize}
\item ADOL-C \cite{Griewank1996a,adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS and LAPACK \cite{lapack}
\item cuSOLVER \cite{cusolver}
\item cuSPARSE \cite{cusparse}
\item Gmsh \cite{geuzaine2009gmsh}
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item ROL \cite{ridzal2014rapid}
\item ScaLAPACK \cite{slug}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item TBB \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

>>>>

The major changes of this release are:
\begin{itemize}
\item Improved support for automatic and symbolic differentiation;
\item Full support for $hp$ adaptivity in parallel computations;
\item Interfaces to the HDF5 file format and libraries.
\item Four new tutorial programs step-61, step-62, step-63, step-64,
  as well as one new code gallery program.
\end{itemize}
These will all be discussed in more detail in the
following section. There are a number of other noteworthy changes in this release:
\begin{itemize}
\item A number of bug fixes and performance improvements to the
  matrix-free framework and related geometric multigrid solvers. In
  particular, the implementation of the Chebyshev iteration, an often
  used smoother in the matrix-free context, has been revised to reduce
  vector accesses. This speeds up matrix-free
  multigrid solvers by up to 10-15\% on geometries with affine
  (parallelogram and parallelpiped) cells, and up to
  5\% on geometries with cells bounded by curved edges and faces.
\marginpar{Luca: Please expand}
\item ParsedConvergenceTable.  
\item The \texttt{FE\_BernardiRaugel} class implements the
  non-standard Bernardi-Raugel (BR) element that can be used as one part of
  a stable velocity/pressure pair for the Stokes equation
  \cite{BR85}. The BR element can be seen as either an enriched
  version of the $Q_1^d$ element with added bubble functions on each
  edge (in 2d) or face (in 3d), or as a reduced version of the $Q_2^d$
  element. It addresses the fact that the $Q_1^d\times Q_0$
  combination is not inf-sup stable (requiring a larger velocity
  space), and that the $Q_2^d\times Q_1$ combination is stable but
  sub-optimal since the velocity space is too large relative to the
  pressure space to provide additional accuracy commensurate with the
  cost of the large number of velocity unknowns. The BR space is
  intermediate to the $Q_1^d$ and $Q_2^d$ spaces.

  The current implementation of the element only works for
  parallelogram meshes due to difficulties associated with the mapping
  of shape functions: The shape functions of the $Q_1^d$ part of the
  element need to be mapped as scalars, as is common for the vector
  components of the $Q_1^d$ element; on the other hand, the
  vector-valued edge bubble functions need to be mapped using the
  Piola transform as is common for the Raviart-Thomas
  element. \dealii{} does not currently have the ability to use
  different mappings for individual shape functions, though this
  functionality is planned for the next release.

\item The \texttt{FE\_NedelecSZ} class is an alternative
  implementation of the ideas behind the N{\'e}d{\'e}elec element. It is based
  on the work of Zaglmayr \cite{Zag06} and overcomes the
  sign conflict issues present in traditional N{\'e}d{\'e}lec
  elements that arise from the edge and face parameterizations used
  in the basis functions. Therefore, this element should provide
  consistent results for general quadrilateral and hexahedral
  elements for which the relative orientations of edges and faces as
  seen from all adjacent cells are often difficult to establish.
  The way this element addresses the sign conflict problem is to assign
  local edges and faces a globally defined orientation. The
  implementation is described in \cite{Kynch2017}.

  \marginpar{Maybe also mention the rtree interfaces?}
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interfaces to the HDF5 file format and libraries}

@@

\marginpar{I'm sure we have new interfaces. HDF5 and the various AD/SD
  libraries come to mind. Please update.}
\dealii can interface with many other libraries:
\begin{multicols}{3}
\begin{itemize}
\item ADOL-C \cite{Griewank1996a,adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS and LAPACK \cite{lapack}
\item cuSOLVER \cite{cusolver}
\item cuSPARSE \cite{cusparse}
\item Gmsh \cite{geuzaine2009gmsh}
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item ROL \cite{ridzal2014rapid}
\item ScaLAPACK \cite{slug}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item TBB \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.
